XXXXX \todo{Le titre !} XXXXX

### 2013-03-24 parts/sa.tex
demo

États focaux possibles: pour tout contexte $\ctx \in \restriction{\PHl}{\Vs(a)}$:
\begin{align*}
  \pfp_\ctx(a) = \{ a_i \in \PHl_a &\mid \exists s \in \ctx, \exists \delta \in \restriction{\Sce}{1}, \PHget{(\ctx \PHplay \delta)}{a} = a_i \\
  & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
\end{align*}

@@

  \item Suppose all children objectives of $P$ are concretizable.
  \begin{itemize}
    \item If $\exists Q \in \Bcont$, then by hypothesis,
      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
      $\muconcr_{s}(P) \neq \emptyset$.
    \item Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bsol$.
      We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
%      \todo{Idée avec les nouvelles defs : au rang 0, on se replace sur un processus de $\pfp$. Au rang n, il existe par saturation un objectif adéquat qui “reprend” la progression.}
      \begin{itemize}
%        \item[*] Let $\zeta_1 = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_1 \in \muconcr_s(\PHobj{\any}{b_i}), \PHget{s \PHplay \delta_1}{a} \in \pfp_s(a)$.
%          If $\PHget{s \PHplay \delta_1}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s \PHplay \delta_1}{a}}{a_k}) \in \Bsat$.
%          By hypothesis, $\muconcr_s(\PHobj{\any}{a_k}) \neq \emptyset$.
%          If $\PHget{s \PHplay \delta_1}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_1 \in \Sce$, $\zeta_1$ can be played in $s \PHplay \delta_1 \PHplay \delta'_1$.
        \item[*] For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
          and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
          By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$.
          If $a \in \cs$, then $\prio(\zeta_n) = 1$ and $\zeta_n$ can be played in $s_n \PHplay \delta_n$ (\ie $\delta'_n = \varepsilon$).
          If $a \notin \cs$ and $b \in \cs$, then there exists a scenario $\widehat{\delta_n}$ so that $b_i \in \pfp_{s_n \PHplay \delta_n \PHplay \widehat{\delta_n}}(b)$.
          Then, by \pref{th:hcscomp}, there is a scenario $\delta' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \widehat{\delta_n} \PHplay \delta'_n$.
          Finally, if $a,b \in \components$, then by \pref{th:hcompcomp}, there is a scenario $\delta' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta'_n$.
      \end{itemize}
      Thus, $\delta = \delta_m \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
  \end{itemize}
\end{itemize}

>>>>

États focaux possibles: pour tout contexte $\ctx \in \restriction{\PHl}{\Vs(a)}$:
\begin{align*}
  \pfp_\ctx(a) = \{ a_i \in \PHl_a &\mid \exists s \in \ctx, \exists \delta \in \restriction{\Sce}{1}, \PHget{(\ctx \PHplay \delta)}{a} = a_i \\
  & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
\end{align*}
Of couse, if $a \in \components$, then $\pfp_\ctx(a) = \PHget{\ctx}{a}$.

@@

  \item Suppose all children objectives of $P$ are concretizable.
  \begin{itemize}
    \item If $\exists (P, Q) \in \Bcont$, then by hypothesis,
      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
      $\muconcr_{s}(P) \neq \emptyset$.
    \item If $\exists (P, Q) \in \Bpriocont$, then by hypothesis,
      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
      $\muconcr_{s}(P) \neq \emptyset$.
    \item Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bsol$.
      We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
%      \todo{Idée avec les nouvelles defs : au rang 0, on se replace sur un processus de $\pfp$. Au rang n, il existe par saturation un objectif adéquat qui “reprend” la progression.}
      \begin{itemize}
%        \item[*] Let $\zeta_1 = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_1 \in \muconcr_s(\PHobj{\any}{b_i}), \PHget{s \PHplay \delta_1}{a} \in \pfp_s(a)$.
%          If $\PHget{s \PHplay \delta_1}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s \PHplay \delta_1}{a}}{a_k}) \in \Bsat$.
%          By hypothesis, $\muconcr_s(\PHobj{\any}{a_k}) \neq \emptyset$.
%          If $\PHget{s \PHplay \delta_1}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_1 \in \Sce$, $\zeta_1$ can be played in $s \PHplay \delta_1 \PHplay \delta'_1$.
        \item[*] For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \delta''_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \delta''_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
          and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
          By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$.
          If $a \in \cs$, then $\prio(\zeta_n) = 1$ and $\zeta_n$ can be played in $s_n \PHplay \delta_n$ (\ie $\delta'_n = \delta''_n = \varepsilon$).
          If $a \notin \cs$ and $b \in \cs$, then there exists a scenario $\delta'_n$ so that $b_i \in \pfp_{s_n \PHplay \delta_n \PHplay \delta'_n}(b)$ (because of the $\Bpriocont$ relation).
          Then, by \pref{th:hcscomp}, there is a scenario $\delta'' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta'_n \PHplay \delta''_n$.
          Finally, if $a,b \in \components$, then by \pref{th:hcompcomp}, there is a scenario $\delta'' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta''_n$ (\ie $\delta'_n = \varepsilon$).
      \end{itemize}
      Thus, $\delta = \delta_m \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
  \end{itemize}
\end{itemize}
